D3692R1: How to Avoid OOTA Without Really Trying

### 2025-06-14 paper/ootavacuous.tex
ootavacuous: Add Section 7.1 forward reference to 7.4
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Some readers may object that our approach does not include any
rigorous definition of semantic dependency itself.
One could address this drawback by turning our DP thesis around
and using it instead as a \emph{definition} of semantic dependency.
In other words, a syntactic dependency could be considered to be semantic
if it is preserved by any valid loose C++
implementation, past, present, or future, real or imagined.
Of course this notion has its own problems, including that it is
extremely nonconstructive and impossible to apply in practice.
However it may be the best we can do with our current understanding
of computing systems.

>>>>

Some readers may object that our approach does not include any
rigorous definition of semantic dependency itself.
One could address this drawback by turning our DP thesis around
and using it instead as a \emph{definition} of semantic dependency.
In other words, a syntactic dependency could be considered to be semantic
if it is preserved by any valid loose C++
implementation, past, present, or future, real or imagined.
Of course this notion has its own problems, including that it is
extremely nonconstructive and impossible to apply in practice,
see for example
Section~\ref{sec:Merging Quasi-Volatile Loads}.
However it may be the best we can do with our current understanding
of computing systems.
